Manuscript

### 2017-07-17 manuscript.Rmd
Standardized variable names.

# Methods
```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_tracts$GEOID10 <- denver_tracts$GEOID_TRAC
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")

boston_tracts <- geojson_read("data/boston_tracts.geojson", what = "sp")
boston_parks <- geojson_read("data/boston_parks.geojson", what = "sp")

nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")

>>>>

# Methods
```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_tracts$GEOID10 <- denver_tracts$GEOID_TRAC
denver_tracts$Phys_Act <- denver_tracts$PhysAct
denver_tracts$CollegeDeg <- denver_tracts$CollegePercent
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")

boston_tracts <- geojson_read("data/boston_tracts.geojson", what = "sp")
boston_parks <- geojson_read("data/boston_parks.geojson", what = "sp")
boston_parks$Park_Acres <- boston_parks$Acreage

nyc_tracts <- geojson_read("data/nyc_tracts.geojson", what = "sp")
nyc_tracts$GEOID10 <- nyc_tracts$GEOID
nyc_tracts$SinglePercent <- nyc_tracts$Single_Percent
nyc_parks <- geojson_read("data/nyc_parks.geojson", what = "sp")
